---
title    : Widgets
subtitle : Slidify Workshop
author   : Ramnath Vaidyanathan
mode     : selfcontained # {standalone, draft}
url      : {lib: "../../libraries"}
hitheme  : solarized_light
editlink : "tutorials/02"
assets:
  js:
    - "http://ajax.googleapis.com/ajax/libs/jqueryui/1.10.3/jquery-ui.min.js"
    - "http://bartaz.github.io/sandbox.js/jquery.highlight.js"
  css: "../02/assets/css/app.css"
--- .segue .dark .nobackground

<q>A widget is a collection of stylesheets, javascripts and layouts that add additional functionality to a slide deck.</q>

```{r echo = F, cache = F}
include<- function(file, prefix = "\t"){ 
    writeLines(paste0(prefix, readLines(file)))
}
```

--- .segue .dark .nobackground

## MathJax

--- .wrappre .centrepre

```{r echo = F, results = 'asis', comment = NA, cache = F}
include("../../demos/widgets/mathjax/index.Rmd", " \t")
```

--- bg:lightgoldenrodyellow

## Try It

<a class='example'>Your Turn</a>

1. Open `demos/widgets/mathjax/index.Rmd`
2. Slidify and Open `index.html`

You can experiment by adding other equations.

--- .segue .dark .nobackground

## Quiz

--- .wrappre .centrepre

```{r echo = F, results = 'asis', comment = NA, cache = F}
include("../../demos/widgets/quiz/index.Rmd", " \t")
```

--- bg:lightgoldenrodyellow

## Try It

<a class='example'>Your Turn</a>

### Basic

1. Open `demos/widgets/quiz/index.Rmd`
2. Slidify and Open `index.html`

### Intermediate

You can find more question types [here](http://slidify.github.io/iquiz). Press `p` on any slide to get the Rmd source, paste it in your `index.Rmd` file and see how it works.
